\SW: Crowd-sourcing the Discovery of Gravitational Lenses

### 2014-05-14 doc/sw-system.tex
Added paper org paragraph to intro

In \Sref{sec:design} we introduce the \sw system, describing and
explaining its various features. We then briefly...

>>>>

This paper is organised as follows. 
In \Sref{sec:design} we introduce the \sw classification interface,  explain
how we use training images, and describe our two stage candidate selection
strategy. We then briefly introduce, in \Sref{sec:data} the particular dataset
used in the first experimental tests of the \sw system, and how we prepared
the images prior to displaying them in the web interface. In \Sref{sec:swap}
we describe our methodology for interpreting the classifications made by the
volunteers, and then present the results of system performance tests 
made on the training images in \Sref{sec:results}.
% In this section, we also investigate the properties of the crowd, to
% understand where the information is coming from.
We discuss the implications of our results for future lens searches in
\Sref{sec:discuss} and draw conclusions in \Sref{sec:conclude}.

% \section{Introduction}
% \label{sec:intro}
% \section{Experiment Design}
% \label{sec:design}
% \subsection{Training}
% \label{sec:design:training}
% \subsection{Stage 1: Initial Classification}
% \label{sec:design:stage1}
% \subsection{Stage 2: Refinement}
% \label{sec:design:stage2}
% \section{Data}
% \label{sec:data}
% \subsection{The CFHT Legacy Survey}
% \label{sec:data:CFHTLS}
% \subsection{Image Presentation}
% \label{sec:data:display}
% \section{Classification Analysis}
% \label{sec:swap}
% \section{Results}
% \label{sec:results}
% \subsection{Crowd Properties}
% \label{sec:results:crowd}
% \subsection{Sample completeness and purity}
% \label{sec:results:sample}
% \section{Discussion}
% \label{sec:discuss}
% \section{Conclusions}
% \label{sec:conclude}
